% Use only LaTeX2e, calling the article.cls class and 12-point type.

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[magyar]{babel}
\pagenumbering{gobble}

\usepackage{graphicx}
\usepackage{float}

\usepackage[T1]{fontenc}

%\usepackage{times}
\usepackage{lmodern}
%\usepackage{cmbright}

\renewcommand\refname{References}

\title{Motorvezérlő modul és kiegészítő elektronika fejlesztése ARM Cortex-M4 processzorra MATLAB segítségével}


\author{Fodor Attila}

\date{\today}

%%%%%%%%%%%%%%%%% END OF PREAMBLE %%%%%%%%%%%%%%%%



\begin{document} 

% Double-space the manuscript.

%\baselineskip24pt

% Make the title.

\maketitle

\begin{abstract}
The paper describes the development of a motor control module in MATLAB and its deployment on the STM32F4-Discovery board and the design of the supplementary electronics of the hardware.
The STM32F4-Discovery is an evaluation board for the STM32F407/417 ARM Cortex-M4 processor family. It features extensive support, including the direct hardwave support from MATLAB using the ST Discovery Board Support Package. Using this extension a motor control unit was designed and tested in Simulink, and direct deployment with MATLAB Embedded Coder was used to program the board and evaluate the software in a working environment.
The development followed the basic principles of Model Based Design, taking advantage of the rapid prototyping capabilities of MATLAB, including the process of code generation, which was documented in detail.
Supplementary electronics were designed to augment the system with wireless connectivity and power electronics, in order to enable the evaluation of the software on a live platform. The design of the electrical circuitry is briefly described, and the programming of the ARM developer board is shown as well.
The performance of the resulting system is inspected using a mobile ground vehicle platform.
\end{abstract}

\clearpage
\pagenumbering{arabic}

\input{mikro}

\bibliography{bibs}
\bibliographystyle{unsrt}



% Following is a new environment, {scilastnote}, that's defined in the
% preamble and that allows authors to add a reference at the end of the
% list that's not signaled in the text; such references are used in
% *Science* for acknowledgments of funding, help, etc.

\end{document}




















